Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-05-08 sections/2homology.tex
.

\begin{proposition}[{\cite[prop.2.2.4.9]{lurie_ha}}]\label{NBR8AQB}
    Let $\mathscr{O}$ be an $\infty$-operad and let $\catC$ be a symmetric monoidal $\infty$-category. Then there is an equivalence
    %
    \begin{equation}
        \mathsf{Fun}^\otimes (\mathsf{Env}(\mathscr{O}), \catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathscr{O}} (\catC),
    \end{equation}
    %
    between the $\infty$-categories of $\mathscr{O}$-algebras in $\catC$ and symmetric monoidal functors from the symmetric monoidal envelope\footnote{A full definition of the symmetric monoidal envelope of an $\infty$-operad can be found in \cite[§2.2.4]{lurie_ha}. For our purposes the two important facts about $\mathsf{Env}$ are that it is a left adjoint to the forgetful functor $U: \cat^\otimes \xrightarrow{} \mathscr{O}\mathsf{p}_{\infty}$, and that the underlying $\infty$-category of $\mathsf{Env} (\mathscr{O})$ is the $\infty$-subcategory of $\mathscr{O}$ spanned by the active morphisms. Informally, the symmetric monoidal structure of $\mathsf{Env}(\mathscr{O})$ is given by concatenating these active morphisms: see \cite[Remark 2.2.4.6]{lurie_ha}.} of $\mathscr{O}$ to $\catC$.
\end{proposition}

>>>>

\begin{proposition}[{\cite[prop.2.2.4.9]{lurie_ha}}]\label{NBR8AQB}
    Let $\mathscr{O}$ be an $\infty$-operad and let $\catC$ be a symmetric monoidal $\infty$-category. Then there is an equivalence
    %
    \begin{equation}
        \mathsf{Fun}^\otimes (\mathsf{Env}(\mathscr{O}), \catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathscr{O}} (\catC),
    \end{equation}
    %
    between the $\infty$-categories of $\mathscr{O}$-algebras in $\catC$ and symmetric monoidal functors from the symmetric monoidal envelope\footnote{A full definition of the symmetric monoidal envelope of an $\infty$-operad can be found in \cite[§2.2.4]{lurie_ha}. For our purposes the two important facts about $\mathsf{Env}$ are that it is a left adjoint to the forgetful functor $U: \cat^\otimes \xrightarrow{} \mathscr{O}\mathsf{p}_{\infty}$, and that the underlying $\infty$-category of $\mathsf{Env} (\mathscr{O})$ is the $\infty$-subcategory of $\mathscr{O}$ spanned by the \emph{active morphisms}, i.e., those which cover maps in $\mathsf{Fin}_\ast$ that send only the basepoint to the basepoint. Informally, the symmetric monoidal structure of $\mathsf{Env}(\mathscr{O})$ is given by concatenating these active morphisms: see \cite[Remark 2.2.4.3/6]{lurie_ha}.} of $\mathscr{O}$ to $\catC$.
\end{proposition}
